Application-Level Regression Testing Framework using Jenkins

### 2017-04-04 manuscript/manuscript.tex
Fixed author and my affiliation.

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Timothy Bouvet, Reuben Budiardja, Galen Arnold}
%xxxx\IEEEauthorrefmark{3} and
%xxxx\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}National Institute for Computational Science\\
National Center for Supercomputing Applications\\
University of Illinois at Urbana-Champaign, 61801\\
National Institute for Computational Sciences\\
The University of Tennessee, Knoxville, TN 37996\\
\{tbouvet@illinois.edu,reubendb@utk.edu,gwarnold@illinois.edu\}}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Electrical Engineering and Computer Science Department\\University of Tennessee, Knoxville, TN 37996\\xx@eecs.utk.edu}
%}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%

\author{
%\IEEEauthorblockN{Christian Y. Cardall, Eirik Endeve, \& Anthony Mezzacappa}
\IEEEauthorblockN{Timothy Bouvet, Galen Arnold}
\IEEEauthorblockA{
National Center for Supercomputing Applications\\
University of Illinois at Urbana-Champaign, 61801\\
tbouvet@illinois.edu, gwarnold@illinois.edu
}

\and

\IEEEauthorblockN{Reuben D. Budiardja}
\IEEEauthorblockA{
National Center for Computational Sciences\\
Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
reubendb@ornl.gov}
}
